---
title: "breakDown2 plots for Titanic data"
author: "Przemyslaw Biecek"
date: "`r Sys.Date()`"
output: rmarkdown::html_document
vignette: >
  %\VignetteIndexEntry{breakDown2 plots for Titanic data}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = FALSE,
  comment = "#>",
  warning = FALSE,
  message = FALSE,
  cache = TRUE
)
```

# Data for Titanic survival

Let's see an example for `breakDown2` plots for survival probability of Titanic passengers.
First, let's see the data, we will find quite nice data from in the `titanic` package.

```{r}
library("titanic")
titanic <- titanic_train[,c("Survived", "Pclass", "Sex", "Age", "SibSp", "Parch", "Fare", "Embarked")]
titanic$Survived <- factor(titanic$Survived)
titanic$Sex <- factor(titanic$Sex)
titanic$Embarked <- factor(titanic$Embarked)
titanic <- na.omit(titanic)
head(titanic)
```

# Model for Titanic survival

Ok, not it's time to create a model. Let's use the Random Forest model.

```{r}
# prepare model
library("randomForest")
rf_model <- randomForest(Survived ~ .,  data = titanic)
rf_model
```

# Explainer for Titanic survival

The third step (it's optional but useful) is to create a DALEX2 explainer for random forest model.

```{r}
library("DALEX2")
predict_fuction <- function(m,x) predict(m, x, type = "prob")[,2]
rf_explain <- explain(rf_model, data = titanic,
                      y = titanic$Survived == "1", label = "RF",
                      predict_function = predict_fuction)
```

# Break Down plot with D3

Ok, not it's time to create a model. Let's use the Random Forest model.

Let's see break down for model predictions for 8 years old male from 1st class that embarked from port C.

```{r}
new_passanger <- data.frame(
  Pclass = 1,
  Sex = factor("male", levels = c("female", "male")),
  Age = 8,
  SibSp = 0,
  Parch = 0,
  Fare = 72,
  Embarked = factor("C", levels = c("","C","Q","S"))
)
```

## Calculate variable attributions

```{r}
library("breakDown2")
rf_la <- local_attributions(rf_explain, new_passanger)
rf_la
```

## Plot attributions with `ggplot2`

```{r}
plot(rf_la)
```

## Plot attributions with `D3`

```{r}
plotD3(rf_la)
```

## Show all features

```{r}
plotD3(rf_la, max_features = 10)
```

## Force OX axis to be from 0 to 1

```{r}
plotD3(rf_la, max_features = 10, min_max = c(0,1))
```


